%-------------------------
% Resume in Latex
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% ATS readable PDF
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    #1 \vspace{-2pt}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small #3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%% RESUME STARTS HERE %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Rakesh Chavan} \\ \vspace{1pt}
    \small
    9619176394 $|$
    \href{mailto:rakesh.chavan776@gmail.com}{\underline{rakesh.chavan776@gmail.com}} $|$
    \href{https://www.linkedin.com/in/rakesh-chavan-05333622b/}{\underline{LinkedIn}} $|$
    \href{https://github.com/rakesh1602}{\underline{GitHub}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\small{
Results-driven Software Engineer with 4 years of experience building scalable backend systems, cloud-native applications, and AI/ML-powered document processing pipelines. Proficient in Java, Spring Boot, Python, and AWS, with hands-on experience delivering high-throughput enterprise solutions in financial services and healthcare domains. Proven track record of optimizing system performance, leading cloud infrastructure deployments, and driving cross-team collaboration in Agile environments.
}

%-----------EXPERIENCE-----------

\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
    {Associate Lead Developer}{July 2025 -- Present}
    {Dexian India Pvt Ltd}{Client - Morningstar, Navi Mumbai, MH}
 \resumeItemListStart
    \resumeItem{Working on financial services platforms with a strong focus on performance, scalability, and system reliability in production environments.}
    
    \resumeItem{Designed and managed AWS infrastructure using ECS, EC2, Lambda, and Data Lake services to support large-scale document processing workflows.}
    
    \resumeItem{Developed and optimized Spring Boot APIs to ensure smooth data flow and seamless integration across multiple enterprise applications.}
    
    \resumeItem{Built and maintained Harness CI/CD pipelines to streamline deployments, improve release stability, and reduce manual operational effort.}
\resumeItemListEnd

\resumeSubheading
    {Jr. Engineer -- Software Development}{Aug 2022 -- June 2025}
    {CrossAsyst Infotech Pvt Ltd}{Navi Mumbai, MH}
    \resumeItemListStart
        \resumeItem{Built backend microservices using Java, Spring Boot, and Golang for enterprise healthcare applications.}
        \resumeItem{Designed REST APIs and optimized Postgres queries for high-volume transaction and document processing systems.}
        \resumeItem{Integrated third-party services and maintained seamless data flow across distributed systems.}
        \resumeItem{Developed ReactJS front-end modules and managed code delivery using Git in Agile environments.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------

\section{Projects}
\resumeSubHeadingListStart

\resumeSubheading
    {DCGateway -- Financial Services}{} 
    {Java, Python, Spring Boot, AWS, React}{}
    \resumeItemListStart
        \resumeItem{Built and optimized document processing APIs used by multiple financial service teams, capable of handling over 300K documents per hour — reducing bottlenecks and enabling teams to scale operations efficiently across the enterprise.}
       \resumeItem{Deployed and maintained Python-based AI/ML document processing models on AWS EC2 and ECS, authored deployment scripts, provisioned supporting infrastructure, and improved system reliability to handle large-scale workloads with NO downtime.}
       \resumeItem{Designed and implemented Apache Airflow DAGs to orchestrate asynchronous processing of large-scale document requests, improving pipeline efficiency and ensuring reliable end-to-end execution across distributed workflows.}
       \resumeItem{Migrated document status and analytics dashboards from a legacy Python-based frontend to Vue3 following MDS standards, achieving a 95\% improvement in load performance and delivering a significantly faster, modern user experience across financial service teams.}
        
    \resumeItemListEnd

\resumeSubheading
    {EHR System -- Healthcare Project (USA)}{}
    {Java, Spring Boot, React, AWS}{}
    \resumeItemListStart
        \resumeItem{Architected and delivered scalable backend microservices using Java and Golang, improving system speed, maintainability, and service reliability across a large-scale US healthcare platform.}
        \resumeItem{Developed secure, standards-compliant REST APIs supporting end-to-end EHR workflows, including CCD/ECD document exchange and FHIR-based third-party integrations with external healthcare providers.}
        \resumeItem{Optimized complex SQL queries to reduce API response times, and implemented comprehensive unit testing to ensure production stability and minimize regression risks.}
        \resumeItem{Collaborated closely with product and QA teams throughout the SDLC to enforce HIPAA compliance, validate business requirements, and drive successful zero-defect production deployments.}
    \resumeItemListEnd



\resumeSubheading
    {}{}
    {}{}
    \resumeItemListStart
 
    \resumeItemListEnd



    

\resumeSubheading
    {AWS Lex ChatBot}{}
    {AWS Lex, Lambda (Java/Python), Spring Boot, Angular}{}
    \resumeItemListStart
        \resumeItem{Designed and deployed a conversational AWS Lex chatbot integrated with Lambda functions and Spring Boot APIs to handle real-time appointment scheduling, updates, and cancellations (CRUD operations).}
        \resumeItem{Built an intuitive Angular-based frontend interface for the chatbot, reducing appointment task completion time from 8--10 minutes to under 1 minute — an 87\% efficiency improvement for end users.}
        \resumeItem{Implemented end-to-end monitoring, structured logging, and usage tracking across Lambda and backend services to enhance system reliability, enable proactive issue detection, and improve operational visibility.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------

\section{Technical Skills}

\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\textbf{Languages:} Java, Python, SQL, Golang,  \\
\textbf{Frameworks:} Spring Boot, React/Vue3 \\
\textbf{Cloud \& DevOps:} AWS (CloudFormation, EC2, ECS, Elastic Load Balancer, SQS, SES, S3 Data Lake, Athena, IAM) \\
\textbf{Developer Tools:} Git, Bitbucket, Jira \\
\textbf{Messaging:} Kafka, SQS, Event-Driven Architecture
}}
\end{itemize}

%-----------CERTIFICATIONS-----------

\section{Certifications}
\resumeSubHeadingListStart

\resumeSubheading
    {AWS Certified Developer -- Associate}{}{}{}

\resumeSubheading
    {Full Stack Java Development -- IT Vedant Education Pvt Ltd}{}{}{}

\resumeSubHeadingListEnd

%-----------EDUCATION-----------

\section{Education}
\resumeSubHeadingListStart

\resumeSubheading
    {Mumbai University}{Navi Mumbai, MH}
    {Bachelor of Engineering}{Aug 2017 -- May 2020}

\resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------

\section{Achievements}
\resumeSubHeadingListStart

\resumeSubheading
    {Top Performer Award}{}{}{}
    \resumeItemListStart
        \resumeItem{Recognized for outstanding contributions, ownership, and consistent high performance across critical production projects.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-------------------------------------------

\end{document}